% Resume, templated off of simple-resume-cv on CTAN. Comments are excluded
% unless there's a significant deviation from the original template.

% Used as-is from CTAN, disabling a few embedded third-party packages that
% caused me problems (hyphenat and datetime2)
% Also removed the page numbering footer.
\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}

% Darken the background a little to be easier on the eyes.
% Color on recommendation from http://bettermotherfuckingwebsite.com/
\usepackage{xcolor}
% #EEEEEE
\definecolor{lightgray}{rgb}{.93,.93,.93}
\pagecolor{lightgray}

\newcommand{\CVAuthor}{Lihu Ben-Ezri-Ravin}
\newcommand{\CVTitle}{Lihu Ben-Ezri-Ravin's resume}
\newcommand{\CVNote}{Document rendered {\today} with {\XeLaTeX}}

\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

\begin{document}

\Title{\CVAuthor}

\begin{SubTitle}
\href{mailto:lihu@tuta.io}
{lihu@tuta.io}
\,\SubBulletSymbol\,
+1\,(484)\,479-6125
\par
\href{https://github.com/lbenezriravin}
{Code (professional): \url{https://github.com/lbenezriravin}}
\,\SubBulletSymbol\,
\href{https://scm.yoloswag.lol/lihu}
{Code (personal): \url{https://scm.yoloswag.lol/lihu}}
\end{SubTitle}

\begin{Body}

\Section
{Skills}
{Skills}
{PDF:Skills}
{\raggedright

\Entry
\textbf{Programming Languages: }
Python,
Bash,
Rust,
Kermit

\Entry
\textbf{Operating systems:}
CentOS/Rocky,
Fedora,
Ubuntu,
Raspberry Pi OS,
VyOS/EdgeOS,
Embedded Linux,
Cisco IOS

\Entry
\textbf{Software: }
git,
Ansible,
systemd,
firewalld,
udev,
Wireshark/tcpdump,
Terraform,
Packer,
Docker/Buildah/Podman,
Buildroot,
{\LaTeX}

\Entry
\textbf{Networking: }
Wi-FI (802.11ac/ax),
VLAN (802.1q),
ARP,
IP,
ICMP,
UDP,
DHCP,
TCP,
TFTP,
DNS,
NTP,
SSH

\Entry
\textbf{SaaS tools: }
AWS (EC2, ECS, ECR, S3, IAM, SNS, Cloudwatch, ACM, RDS),
Jenkins,
TeamCity,
Artifactory

%\Entry
%\textbf{Other standards: }
%YAML,
%HCL,
%RS232,
%SCPI,
%OpenAPI,
%OCI

}

\Section
{Experience}
{Experience}
{PDF:Experience}

\Entry
\textbf{Portal Instruments}
\hfill
\DatestampYM{2022}{04} --
\DatestampYM{2022}{12}
\Gap
\textit{Senior DevOps Engineer}
\Gap
\BulletItem
Converted the existing manually-configured VM-based CI to an OCI-compliant
containerized system. Documented and automated the process using Terraform.
\BulletItem
Spearheaded company-wide security compliance efforts. Targeted specific
immediate business requirements, using ISO 27001 and SOC 2 as reference.
\BulletItem
Collaborated with senior developers to establish code standards for
Python scripts. Automated them and worked directly with junior developers and
electrical/mechanical engineers to convert existing projects.

\BigGap

\Entry
\textbf{Starry Inc.}
\hfill
\DatestampYM{2017}{02} --
\DatestampYM{2022}{03}
\Gap
\textit{Principal Systems Software Engineer}
\Gap
\BulletItem
Wrote firmware in Rust for embedded Linux on Starry radios allowing for
automatic self-configuration in the field.
\BulletItem
Shipped 8 distinct products across a 5 year tenure at Starry.

\BigGap
\textit{Manager, Systems Software Tooling}
\Gap
\BulletItem
Owned the firmware build infrastructure, a CI/CD pipeline using Jenkins and
Kubernetes. Over 6 months, cut build time by 50\%, from 4 hours down to 2.
\BulletItem
Maintained the nightly test automation infrastructure, scaling it with
the ballooning number of new products, tests, and test harnesses.
\BulletItem
Supported automated provisioning, updates, security patches, and
technical support for engineering testbeds and manufacturing systems.
%\BulletItem
%Shipped one new product

\BigGap
\textit{Manager, Internet Firmware Validation}
\Gap
\BulletItem
Oversaw the hiring process, growing the team from 4 to 9 engineers over 10
months.
%\BulletItem
%Wrote product requirements and held engineers accountable for them.
\BulletItem
Expanded test coverage while delivering on tight deadlines and
communicating progress to C-suite.
\BulletItem
Built and shipped a test storage and reporting solution using MariaDB.
%\BulletItem
%Shipped three new products

\BigGap
\textit{Senior Systems Integration and Validation Engineer}
\Gap
\BulletItem
Designed and wrote full-system test software for manufacturing,
including controls for a variety of hardware components over RS232,
USB, and ethernet.
%\BulletItem
%Wrote, maintained, and supported software for automated depot upgrades
%intended for non-technical users.
%\BulletItem
%Developed and carried out the technical software interviews for new
%team hires. Succesfully hired dozens of employees over 4 years.
\BulletItem
Mentored 8 Northeastern co-ops over 3 years, each of which took ownership of
long-term, critical projects. Two went on to take full-time positions with
Starry.
\BulletItem
Built and expanded an internal test network and testbed automation
infrastructure to the manufacturing line overseas. Maintained 24/7 uptime over
7 time zones.
%\BulletItem
%Shipped two new products

\BigGap
\textit{Systems Integration and Validation Engineer}
\Gap
\BulletItem
Set up automation from scratch for administrating and documenting
state on test harnesses using Ansible.
%\BulletItem
%Built out an internal network for testing and development, as well
%as support for other engineering teams.
%\BulletItem
%Wrote, maintained, and supported test automation for manufacturing.
\BulletItem
Migrated existing projects to Python 3.
\BulletItem
Implemented team code standards (formatting, pylint, mypy, documentation,
etc.) and automated their enforcement in CI with Jenkins.

\BigGap
\textit{Junior Software Engineer, QA}
\Gap
\BulletItem
Wrote unit and integration tests for firmware on Starry radios.
\BulletItem
Built, maintained, and automated physical test harnesses.
%\BulletItem
%Shipped two new products

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\textbf{Swarthmore College}
\Gap
B.A. in Computer Science and Biology

\end{Body}

\end{document}
